---
title: "Investigating_GIs"
author: "Ben Temperton"
date: "05/11/2018"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(ggsci)
library(magrittr)
source('useful.functions.R')
```

```{r}

tmp <- read_tsv('./data/hybrid.viral.vs.L4.sorted.98pc.windows.merged.txt')
tmp$type <- 'hybrid'
tmp$cutoff <- 98

tmp2 <- read_tsv('./data/hybrid.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp2$type <- 'hybrid'
tmp2$cutoff <- 95

tmp3 <- read_tsv('./data/hybrid.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp3$type <- 'hybrid'
tmp3$cutoff <- 92

tmp4 <- read_tsv('./data/short.viral.vs.L4.sorted.98pc.windows.merged.txt')
tmp4$type <- 'short'
tmp4$cutoff <- 98

tmp5 <- read_tsv('./data/short.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp5$type <- 'short'
tmp5$cutoff <- 95

tmp6 <- read_tsv('./data/short.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp6$type <- 'short'
tmp6$cutoff <- 92

tmp7 <- read_tsv('./data/long.viral.vs.L4.sorted.98pc.windows.merged.txt')
tmp7$type <- 'long'
tmp7$cutoff <- 98

tmp8 <- read_tsv('./data/long.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp8$type <- 'long'
tmp8$cutoff <- 95

tmp9 <- read_tsv('./data/long.viral.vs.L4.sorted.95pc.windows.merged.txt')
tmp9$type <- 'long'
tmp9$cutoff <- 92


final_df <- tmp %>% 
  bind_rows(tmp2) %>% 
  bind_rows(tmp3) %>%
  bind_rows(tmp4) %>%
  bind_rows(tmp5) %>%
  bind_rows(tmp6) %>%
  bind_rows(tmp7) %>%
  bind_rows(tmp8) %>%
  bind_rows(tmp9)

summary_df <- final_df %>% group_by(type, cutoff) %>% 
  summarise(median_length=median(gi_length), 
            IQR_length=IQR(gi_length),
            number_of_GIs=n(),
            max_GI_length=max(gi_length))

```

```{r}
library(ggbeeswarm)
final_df$cutoff<-as.factor(final_df$cutoff)
final_df$type<-factor(final_df$type, levels=c('short', 'hybrid', 'long'))
p1<- ggplot(final_df, aes(y=gi_length, x=type, fill=cutoff)) +
  geom_boxplot() + 
  coord_trans(y = "log10") +
  labs(y='Length of Genomic Island (bp)', x='Assembly Type') +
  theme(axis.title = element_text(size=16, face='bold'),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=16)) + 
  scale_fill_npg()
```

```{r}
per_kb<- final_df %>% group_by(type, cutoff, contig, length) %>%
  summarise(tot_length=sum(gi_length), num_GIs=n()) %>%
  mutate(kb_gi_per_kb_genome=(tot_length/1000)/(length/1000))

p2<- ggplot(per_kb, aes(y=kb_gi_per_kb_genome, x=type, fill=cutoff)) +
  geom_boxplot() + 
  #coord_trans(y = "log10") +
  labs(y='Kbp of GI per Kbp of Genome', x='Assembly Type') +
  theme(axis.title = element_text(size=16, face='bold'),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=16)) + 
  scale_fill_npg()
```

```{r}
per_kb$combined_factor<-with(per_kb, interaction(type, cutoff))
pairwise.wilcox.test(per_kb$kb_gi_per_kb_genome, per_kb$combined_factor, p.adj='bonferroni')
```

```{r}
final_df$combined_factor<-with(final_df, interaction(type, cutoff))
pairwise.wilcox.test(final_df$gi_length, final_df$combined_factor, p.adj='bonferroni')
```

```{r}
per_kb %>% group_by(type, cutoff) %>% summarise(total_genome_length=sum(length), total_num_gis=sum(num_GIs), total_length_GIs=sum(tot_length)) %>% mutate(tot_gi_kb_per_genome_kb=(total_length_GIs/1000)/(total_genome_length/1000), num_GIs_per_kb=total_num_gis/(total_genome_length/1000))
```

```{r}
library(boot)
boot_median <- function(x) {
  median(sample(x, replace=TRUE))
}

calculate_effect_size<-function(x, y, n=1000, conf_level=0.95){
  lower_percentile <- (1-conf_level)/2
  upper_percentile <- 1-((1-conf_level)/2)
  
  x_median<-replicate(n, boot_median(na.omit(x)))
  y_median<-replicate(n, boot_median(na.omit(y)))
  diff <- y_median - x_median
  low_CI <- quantile(diff, probs=lower_percentile)
  high_CI <- quantile(diff, probs=upper_percentile)
  return(list(effect=round(median(diff), digits=2), low_CI=round(low_CI, digits=2), high_CI=round(high_CI, digits=2)))
}


